---
title: "Creating a lesson"
teaching: 10
exercises: 2
---

```{r setup, includes = FALSE, warning = FALSE, message = FALSE}
#| setup
#| echo: false
#| includes: false
#| warning: false
#| message: false
if (fs::dir_exists("my-lesson")) fs::dir_delete("my-lesson")
```


:::::::::::::::::::::::::::::::::::::: questions 

- How do you write a lesson using RMarkdown and `{sandpaper}`?

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Explain how to use markdown with the new lesson template
- Demonstrate how to include pieces of code, figures, and nested challenge blocks

::::::::::::::::::::::::::::::::::::::::::::::::

## Introduction

This is the new Carpentries template. It is written in [RMarkdown][r-markdown],
which is a variant of Markdown that allows you to render code inside the
lesson. Please refer to the [lesson
example](https://carpentries.github.io/lesson-example) for full documentation.


You can create a new lesson by loading {sandpaper} and running `create_lesson()`:

```{r}
library("sandpaper")
create_lesson("my-lesson", open = FALSE)
```

Now that we have a lesson, we can build it with `build_lesson()`, which will
produce a lot of output, but when we build it again, it will produce 
significantly less output.

```{r}
build_lesson("my-lesson", preview = FALSE, quiet = FALSE)
build_lesson("my-lesson", preview = FALSE, quiet = FALSE)
```


::::::::::::::::::::::::::::::::::::: keypoints 

 - Use `sandpaper::create_lesson()` to create a lesson
 - Use `manage_dependencies()` to manually add dependencies to a lesson
 - Preview your lesson with `build_lesson()`
 
::::::::::::::::::::::::::::::::::::::::::::::::

